---
title: "Assignment 2 [Big Data Analytics for Business]" 
output: html_notebook
---

### Case study [Data Wrangling] - Bank Marketing Data Set
For this homework task, read the instructions and answer the questions below.

The dataset was originally published in a research paper:
*S. Moro, P. Cortez and P. Rita. A Data-Driven Approach to Predict the Success of Bank Telemarketing. Decision Support Systems, Elsevier, 62:22-31, June 2014*


<span style="color:red">The data is related with direct marketing campaigns of a Portuguese banking institution. 
<br/>The marketing campaigns were based on phone calls. 
<br/>Often, more than one contact to the same client was required, in order to access if the product (bank term deposit) would be ('yes') or not ('no') subscribed.</span>


For more information on the dataset and each column's description, visit: <http://archive.ics.uci.edu/ml/datasets/Bank+Marketing>


### Required Packages
- tidyverse
- shimr


----------------------------------------------
**1. Load the libraries and download the dataset**
```{r}
library(tidyverse)

data_url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/00222/bank.zip"
temporaryFile <- tempfile()
download.file(data_url, temporaryFile)
```


**2. Extract (unzip) the file *bank.csv* from the *temporaryFile* variable**
```{r}
unzip(temporaryFile, "bank.csv")
```


**3. Load the dataset**

_read_csv() and read_tsv() are special cases of the more general read_delim(). They're useful for reading the most common types of flat file data, comma separated values and tab separated values, respectively. read_csv2() uses ; for the field separator and , for the decimal point. This format is common in some European countries._

```{r, echo=FALSE}
bankData <- read_csv2("bank.csv")
```


**4. View the first 5 observations(rows)**

```{r}
head(bankData, 5)
```


**5. To print out the dataset/tibble's variable (column) names**
```{r}
bankData %>%
  names()
```


**6. Let us briefly summarize the dataset (a statistical overview)**
```{r}
summary(bankData)
```



**7. Explaratory Data Analysis (using the *skimr* library)**

Load the skimr library

Evaluate the data distribution - Test for empty columns (variables)
```{r}
library(skimr)

#distribution of data
skimResults =
  bankData %>%
  skim()

#print the results
skimResults
```
The results above give us basic summary statistics on each of the 7 columns(variables): 

```{r}
skimResults%>%
  names()
```

```{r}
skimResults %>%
  select(skim_variable,n_missing)
```



### Questions
<span style="color:red">
Understand each variable (column) and answer the question. Indicate the code you used to obtain each result.<br/>(Submit your answers as an .Rmd file) 
</span>

**Q1.** How many clients **subscribed** to the bank's product (term deposit)?


**Q2.** Which **job category** do majority of the bank's clients belong to?


**Q3.** How many **unemployed** people who were contacted in **November** have a **housing loan**?


**Q4.** Which **month** recorded the **least calls** to **retired clients** (i.e. pensioners)?


**Q5.** How many students are **less than 25 years old**?


**Q6.** Which **job category** did the bank perform many **contact campaigns (phone calls)** ?


**Q7.** Which **educational qualification** does most client's whose **campaign outcomes failed** belong to?



-----------------------------------------------------

<span style="float:right">eagbozo@urfu.ru</span>